Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-01-18 analysis/paper/paper.Rmd
get different CV test result from another project, but the same data?

Ceramics analyzed in this paper come from 40 units (4m by 4m) sampled from the largest excavation section at Kiwulan, northeastern Taiwan (Figure \@ref(fig:KWL-map), Figure \@ref(fig:KWL-sam-area)). Kiwulan is situated on a hill near a riverside at the northern margin of Yilan, which is characterized by a triangular alluvial plain facing eastwards the Pacific with high mountains on three other sides. Yilan is an ideal context to study peripheral colonial influence because it was relatively isolated by natural barrier that reduced frequency of direct contact with the Europeans presences, the Spanish and the Dutch settled in northern Taiwan. The chronology of Kiwulan consists of two cultural components, the upper component and the lower component, with a sterile layer in between [@Chen2007]. This paper focuses on the upper component dated from AD 1350 to AD 1950, covering the late Iron Age and the historical period defined by the European presence in Taiwan in the early 17th century. The Dutch firstly came and occupied southern Taiwan in 1624 and then the Spanish occupied northern Taiwan in 1626. In 1642, the Spanish was expelled by the Dutch, who took over their forts in northern Taiwan. Since then, western Taiwan was mostly under the colonial rule of the Dutch until 1662 when the Kingdom of Tungning in Taiwan was founded by Koxinga, a loyalist of the Ming dynasty of China [@Andrade2007].

@@

```{r, KWL-sam-area, fig.cap = "Map showing the largest section of excavation areas at Kiwulan, and the distribution of forty squares sampled in this paper presented in red with square ID number. Small dots represent the location of post-holes. Each square is 4 x 4 m", fig.width=image_width_2_col_inch}
knitr::include_graphics(here("analysis", "figures", "KWL-excavation-map.jpg"))
```

@@

PC1_PC2_cv_tests <-
bind_rows(PC1_cv_tests, 
          PC2_cv_tests, .id = "PC") %>% 
  mutate(PC = str_glue('PC{PC}')) %>% 
  mutate(PC = as.character(PC))

>>>>

Ceramics analyzed in this paper come from 40 units (4m by 4m) sampled from the largest excavation section at Kiwulan, northeastern Taiwan (Figure \@ref(fig:KWL-map); Figure \@ref(fig:KWL-sam-area)). Kiwulan is situated on a hill near a riverside at the northern margin of Yilan, which is characterized by a triangular alluvial plain facing eastwards the Pacific with high mountains on three other sides . Yilan is an ideal context to study peripheral colonial influence because it was relatively isolated by natural barrier that reduced frequency of direct contact with the Europeans presences, the Spanish and the Dutch settled in northern Taiwan. The chronology of Kiwulan consists of two cultural components, the upper component and the lower component, with a sterile layer in between [@Chen2007]. This paper focuses on the upper component dated from AD 1350 to AD 1950, covering the late Iron Age and the historical period defined by the European presence in Taiwan in the early 17th century. The Dutch firstly came and occupied southern Taiwan in 1624 and then the Spanish occupied northern Taiwan in 1626. In 1642, the Spanish was expelled by the Dutch, who took over their forts in northern Taiwan. Since then, western Taiwan was mostly under the colonial rule of the Dutch until 1662 when the Kingdom of Tungning in Taiwan was founded by Koxinga, a loyalist of the Ming dynasty of China [@Andrade2007].

@@

```{r, KWL-sam-area, fig.cap = "Map showing the largest section of excavation areas at Kiwulan, and the distribution of forty squares sampled in this paper presented in red with square ID number. Small dots represent the location of post-holes. Each square is 4 x 4 m", fig.width=image_width_2_col_inch}
knitr::include_graphics(here::here("analysis", "figures", "KWL-excavation-map.jpg"))
```

@@

PC1_PC2_cv_tests <-
bind_rows(PC1_cv_tests, 
          PC2_cv_tests, .id = "PC") %>% 
  mutate(PC = str_glue('PC{PC}')) %>% 
  mutate(PC = as.character(PC)) %>% 
  mutate_at(c("MSLRT", "p_value"), round, 4)
